???A quantitative framework for investigating the reliability of network construction

### 2017-11-15 manuscript/CI_interactions.tex
fixed some compiling errors, supplemental still isn't perfect
added Tomas' comments

    % Present Salix data with holes as an example of uncertainty in data. Focus just on the white and grey, ignore uncertainty in the blacks

    Ecological networks-- which include antagonistic food webs and host-parasite networks as well as plant-pollinator and plant-frugivore mutualist networks --are usually considered to be static representations of the communities and interactions they describe. That is, whether the network is assembled based on aggregated data, a single intensive "snapshot" sample, or expert knowledge, interactions are assumed to occur at constant frequencies~\citep{Olesen2011a}. This assumption conflicts with known variation in interactions over time~\citep{Kitching1987,Olesen2011a} and space~\citep{Kitching1987,Baiser2012} and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}. Taking the variation in interaction frequencies into account would therefore represent a substantial increase in the realism of ecological networks as representations of ecological communities.

    Efforts to account for variance in interaction frequencies are complicated by the fact that not only interaction frequencies but network structure vary over space and time. Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}. The removal of a species from a site will obviously also remove its interactions. Interactions can also be lost, however, if participating species remain present but do not co-occur temporally or are too rare to detect each other~\citep{Tylianakis2010}, or through changes to individual preferences~\citep{Fodrie2015}. Several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}). Despite this, the acknowledgement that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty of ecological interactions and of sampling.

    The main objective of this study is to develop analytical tools that could be used to better represent the uncertainty in the estimation of pairwise interaction probability. We start with the description of a new Bayesian approach to estimate ecological interactions and of a related R package. [[We first illustrate the framework with a simple quantitative example. Next, we use the framework to provide analytical criteria for improving the sampling of rare interactions. Finally, we discuss the implications of uncertainty in the estimation of pairwise interactions on the properties of ecological networks.]][[Order has probably changed.]] Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in ecological networks.
    % List of sections may not be accurate any more. Update when paper reaches its final form.

\section*{Different uncertainties in computing a network}

THIS SECTIONS BUILDS ON THE SALIX DATA TO ILLUSTRATE THE GAPS THERE ARE IN THE METHOD. DESPITE THE INTENSITY OF THE SAMPLING, THERE ARE SEVERAL HOLES.[[Still necessary? If so, we should flesh this out into a paragraph.]]

  It is getting more and more common to represent interactions as probabilities in theoretical models of network structure. For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a gaussian probability function is used to represent the niche by~\citet{Williams2010}. \citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species. Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.,~\citealp{Rohr2016}). There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version~\citep{Poisot2016}. But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.

  As a start, we will consider how we could naively quantify interaction probability and its associated uncertainty for an interaction that has not yet been observed. We consider that a pair of species have been observed $n$ times co-occurring at one location, and the number of times they have been observed interacting is $k = 0$. We aim to evaluate the uncertainty of this interaction. The occurrence of an interaction is a Bernoulli trial. Consequently, the number of success $k$ over $n$ trials will follow a binomial distribution:

  \noindent The parameter $\lambda$, the probability of observing an interaction over an infinite time interval and area, is the quantity we want to estimate from empirical data. 
  The maximal likelihood estimate (MLE) of $\lambda$ is straightforward to find given $k$ and $n$. It is simply equal to:

  The variance of a Bernoulli experiment is simply $n\lambda$(1-$\lambda$). It is important to remember this variance reports the variability of the number of success $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$.
  Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval}. Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks. First, $\lambda$ is a random variable with a given uncertainty and whose distribution is unknown, it is not a single point estimate. This means that even if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. It means that no interaction is the most likely situation but there is nonetheless a significant chance that the two species could interaction. In contrast with the situation where $k>0$, when we are sure that an interaction is feasible, 
  % (in which case, the ratio $k/n$ is smaller than $n$ because of detection and process uncertainty),  % This parenthetical makes the sentence very long. Is it necessary?
  we are not sure that absence of interactions is caused by $L=0$. Second, and most importantly, the number of trials $n$ might be very low in many instances (and some pairs of species might even not be documented once). Consequently, the uncertainty in the estimation of $\lambda$ might be considerable. We illustrated in Fig. X how the estimate of $\lambda$ could vary with sampling size using the Clopper-Pearson interval. It shows that the 95\% confidence interval requires a significant amount of sampling in order to be sure that species are not interacting. 
  % Is the Clopper-Pearson interval the one in Dom's code snippets? If so, this is Fig.~\ref{Salix_cdfs}

  The situation where $k = 0$ is also problematic because we have very little information with which to estimate $\lambda$, in particular when $n$ is also small. We therefore propose a Bayesian approach to solve this problem, building on two relevant features of such statistics : posterior distribution of parameter estimates and usage of prior information. Before moving to this direction, we will first take time to better describe what is exactly meant by an interaction probability and appropriately define sources of uncertainty.

\section*{Why do some interactions not occur?}

  What does this question mean exactly? We consider that there are three nested levels of uncertainty making the occurrence of any interaction a stochastic process:

@@

    First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics to interact. We define the probability of an interaction $L$ as $P(L)=\lambda$. Obviously, because $k=0$, it is very likely that they cannot interact even if there were no time or environmental constraints preventing the interaction. But it is nonetheless possible that the interaction is a rare phenomenon that has never been documented before. This source of uncertainty is the one documented by trait-matching models~\citep{}. It arises because every model is imperfect and lacks information (i.e. traits) about the constraints on the interaction. In other words, with sufficient sampling and all information accessible, this interaction probability should either tend to 0 or to 1 and the uncertainty vanish.

@@

    It could be that the interaction is feasible, i.e. $L=1$, but that it does not occur at a given location or moment in time because there are local constraints preventing it from occurring. We define the realisation of the interaction process $X$ given that the interaction is feasible as a stochastic process with associated probability $P(X|L)=\chi$. This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions~\citep{}. We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).

@@

    \subsection*{What is an observation of "no interaction"?}

@@

  A simple example will illustrate the problem: assume that we want to infer the probability of an interaction between two species, A and B. Now assume that in reality, interaction between A and B is completely impossible (i.e. the true $\lambda$= 0). Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal (very) little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1 (see following section). For 5 observations, this confidence limit will still extends to 0.5. Only with thirty observations will it shrink to 0.1. Thus, adding (many) more observations is certainly useful in controlling uncertainty due to stochasticity inherent in the process itself.

@@

  The pattern of Fig.~\ref{upper_limits} should be compared to the frequency of co-occurrence of taxa in the Salix-galler data set. Here, most (3986 out of 4992) pairs of species are never found co-occurring, and for species found co-occurring the number of co-occurrences was generally low (Fig.~\ref{histograms}A). Among the species which did sometimes interact when co-occurring, the incidence of interaction was actually low. Only 141 pairs of species were observed interacting: of these, 26 were observed interacting only once and 48.2\% were observed interacting five or fewer times (Fig.~\ref{histograms}B). Thus, even in the most extensive data set that we could think of, limited sampling is clearly a major source of uncertainty.

@@

  The bottom line is that separating different sources of uncertainty is difficult indeed. In the best of all possible worlds, we might use an experimental approach to estimate detection uncertainty by creating replicate cases where the interaction really occurs and then evaluating the fraction of cases where the interaction is detected. Yet, as anyone attempting these experiments will know, most interaction partners are notoriously unwilling to collaborate. Gallers refuse to lay eggs on their host plants in captivity (ref ref) and parasitoids decline to attack their hosts when experimentally introduced (Gariepy 2017; ref ref). If we introduce only one of the components (as in the cases where we expose a set of hosts to parasitism; ref ref; Gripenberg et al. xxx) then we are already confounding multiple levels of uncertainty since it is not certain whether the interaction will occur or whether we can detect it. To perform these experiments in a comprehensive and reliable manner, we will then need to replicate a large number of interactions in a comprehensive experiment across space. This type of “cafeteria experiments in space” is not only unfeasible, but also undermines our original objective: If the local occurrence of interactions is uninformative regarding the underlying probabilities of occurrence, then is not likely to be worthwhile collecting these local interaction matrices in the first place. <deep sigh and forget that section? >

  As an alternative to abandoning empirical networks or continuing to ignore the uncertainty inherent in undetected observations, we propose that some insight regarding the detectability of interactions between species not found co-occurring may be gained from data on other species between which interactions are known to be feasible. If we use this information obtain the joint probability of detection and process (e.g. to glean information regarding at how many sites the species are found interacting across the entire dataset), and assuming that most of this pattern is due to variation in detection rate, then insights into the incidence of interactions between species may be gleaned from the accumulation rate of positive interactions at sites were interaction is possible (i.e. with at least one observation of a positive interaction) [this reasoning to be further formalised]

@@

      We here adopt a Bayesian approach to estimate the distribution of the parameter $\theta$. According to Bayes principle, the posterior distribution of $\theta$ is:

@@

      \begin{figure}[ht]
        \label{Salix_pdfs}
        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-parasitoid networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting. Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution (N=0 observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times. The distribution narrows and approaches zero as the sample size increases. \textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-parasitoid component.}
        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
        \end{figure}

@@

          It is possible to estimate the probability of interaction between a pair of species if there is knowledge of their traits and some functions relating trait matching to interaction probability~\citep{Morales-Castilla2015}. There are several techniques available to perform this inference of interaction probability~\citep{} (REFS). Note that in this case the prior might not be beta distribution and numerical methods might be required to compute the posterior distribution.

@@

    The exercise exemplified above yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1. Note the special case where there is no observation of the two species co-occurring and failing to interact, $n = 0$. In this situation, the posterior distribution converges to the prior distribution.

@@

    It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}. Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$; the remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one. It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics. Computation of these metrics involves non-linear functions and therefore, because of Jensen's inequality (which states that the average of non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty in $\lambda$s could bias both the mean and variance of a network metric. For instance, assume that among all pairs of species with few observed co-occurrence there are many pairs which truly interact.    If we begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution. While we can, as described above, calculate these network metrics using fixed estimates for $\lambda$ no analytical solution currently exists for uncertain $\lambda$. Instead we must rely on computer simulations. In the following section, we will provide an example with the Salix dataset and show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics. We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed fixed entities.

@@

      We use an extensively sampled \emph{Salix}-galler-parasitoid meta-network as a case study. This dataset consists of a single community type sampled across Europe, including willow (\emph{Salix}) species, willow-galling sawflies (Hymenoptera, Tenthredinidae, Nematinae, Euurina), and their natural enemies (hymenopteran parasitoids and coleopteran, lepidopteran, dipteran, and hymenopteran inquilines). The data was collected over 29 years (1982-2010) at 374 unique locations across Europe ranging from Sicily to the Arctic. Including repeated visits to a number of sites, the data set contains 641 site-visits, each of which can be considered as a network in its own right, but here we consider each network as an independent sample from which to build the meta-network. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes and 126 natural enemy nodes. Interactions were determined by dissecting and rearing gall inhabitants from 165,424 galls. Something about how the suitability of this for what we're doing. E.g: The high spatiotemporal resolution of this network and the 641 site-visits which can be considered as independent samples of the network make this dataset particularly well suited for testing this method.

@@

      With species $i$ and $j$ co-occurring at all 374 sites and never being observed to interact, the maximum likelihood expectation for the probability of an interaction $ij$ is very close to 0 and the variance about this estimate is very narrow. In most cases, however, species $i$ and $j$ did not co-occur at so many sites and our posterior mean and variance retain some influence of the prior. Nevertheless, as the number of observed co-occurrence increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).

@@

      As well as obtaining posterior means and variances, it is possible to calculate a 95\% credible interval about the posterior mean. This is again straightforward to do in R (see the function ``credible interval" in \emph{Appendix S2}). Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrences without any observed interaction (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases. In no case, however, does the confidence interval include 0. Even for a pair of species which appeared together in all 374 sites but were never observed interacting, the confidence interval (0.001, 0.018) comes close to, but does not include zero (Table~\ref{interval_table}).

@@

      \begin{table}[h]
        \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Barbour2016,Barbour2016Dryad}.}
        \label{interval_table}
        \begin{tabular}{l | c c | c c }
        \multirow{2}{*}{N} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-parasitoid}\\
         & Lower bound & Upper bound \\
        \hline
        0   & 0.152 & 0.931 & 0.008 & 0.364 \\
        1   & 0.110 & 0.843 & 0.007 & 0.337 \\
        2   & 0.087 & 0.760 & 0.006 & 0.313 \\
        5   & 0.053 & 0.573 & 0.005 & 0.258 \\
        10  & 0.033 & 0.400 & 0.004 & 0.200 \\
        15  & 0.023 & 0.306 & 0.003 & 0.163 \\
        20  & 0.018 & 0.247 & 0.003 & 0.137 \\
        25  & 0.015 & 0.208 & 0.002 & 0.119 \\
        50  & 0.008 & 0.115 & 0.001 & 0.071 \\
        100 & 0.004 & 0.061 & 0.001 & 0.039 \\
        150 & 0.003 & 0.041 & \textless0.001 & 0.027 \\
        200 & 0.002 & 0.031 & \textless0.001 & 0.021 \\
        \hline
        374 & 0.001 & 0.017 & \textless0.001 & 0.011 \\
        \hline
        \end{tabular}
        \end{table}

@@

>>>>

    % Present Salix data with holes as an example of uncertainty in data. Focus just on the white and grey, ignore uncertainty in the blacks
    In modern community ecology, species assemblages are increasingly described and analyzed as networks~\citep{Thompson2012,RecentReviews}. Such representations offer convenient summaries of how communities are constructed since they simultaneously account for species composition and their interactions. Species are represented as nodes, hence a tabulation of the nodes present and of their relative abundances form the basis for traditional metrics of community composition. On top of this information, interactions are represented by links, so that networks provide additional, higher-order information on community structure. Metrics of how networks are structured at the level of links emerging from individual species (such as link density, vulnerability and degree distribution), and of network-level structure (such as nestedness, connectance and modularity), then offer key descriptors of how species interactions are structured across the globe~\citep{Schleuning2012,Morris2014,XX}, valuable proxies of community dynamics~\citep{Thebault2010,XX} and [many other nice things]. Thus, deriving robust descriptors of network properties is a key objective for modern community ecology.

    Importantly, empirical descriptions of ecological networks are usually considered to be static representations of the communities and interactions they describe. That is, whether the network is assembled based on aggregated data, a single intensive "snapshot" sample, or expert knowledge, interactions are assumed to occur at the same frequencies wherever and whenever the network is observed~\citep{Olesen2011a}. This assumption conflicts with known variation in interactions over time~\citep{Kitching1987,Olesen2011a} and space~\citep{Kitching1987,Baiser2012} and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}. Taking the variation in interaction frequencies into account would therefore represent a substantial increase in the realism of ecological networks as representations of ecological communities.

    Efforts to account for variance in interaction frequencies are complicated by the fact that not only interaction frequencies but network structure vary over space and time. Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}. The removal of a species from a site will obviously also remove its interactions. Interactions can also be lost, however, if participating species remain present but do not co-occur temporally or are too rare to detect each other~\citep{Tylianakis2010}, or through changes to individual preferences~\citep{Fodrie2015}.

    Beyond "true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}). Despite this, the acknowledgement that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.

    In this study, we develop analytical tools to capture the uncertainty in the estimation of pairwise interaction probability. To define the problem, we first discuss the pervasive implications of uncertainty in the estimation of pairwise interactions on the properties of ecological networks. We then define a framework which identifies and dissects the different contributions to uncertainty of interaction. We illustrate this framework with a simple quantitative example. Next, we use the framework to provide analytical criteria for improving the sampling of rare interactions. Finally, we offer tangible recommendations for improved descriptors of ecological interactions. Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in ecological networks.
    % List of sections may not be accurate any more. Update when paper reaches its final form.

\section*{Why do some interactions \emph{not} occur?}

  To define the problem associated with describing ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing an interaction networks. This ecologist will be interested in generating a description of the blocks present, and the links between them (Roslin and Majaneva 2017). In other words, he or she seeks to fill in a matrix of species by species interactions. Importantly, the information sought is as much in the presence of given links as in the absence of others. An observed link will always remain an observed link, but to why given links are not observed, there may be multiple contributions. Thus, we will set off by contemplating what factors may contribute to links missing from the matrix. We consider that there are three nested levels of uncertainty making the occurrence of any interaction a stochastic process:

@@

    First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics to interact. We define the probability of an interaction $L$ as $P(L)=\lambda$. Obviously, because $k=0$, it is very likely that they cannot interact even if there were no time or environmental constraints preventing the interaction. But it is nonetheless possible that the interaction is a rare phenomenon that has never been documented before. This source of uncertainty is the one documented by trait-matching models~\citep{}. It arises because every model is imperfect and lacks information (i.e. traits) about the constraints on the interaction. In other words, with sufficient sampling and all information accessible, this interaction probability should either tend to 0 or to 1 and the uncertainty vanishes.

@@

    It could be that the interaction is feasible, i.e. $L=1$, but that it does not occur at a given location or moment in time because there are local constraints preventing it from occurring. We define the realisation of the interaction process $X$ given that the interaction is feasible as a stochastic process with associated probability $P(X|L)=\chi$. This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions~\citep{}. 
    % We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).

@@

    % \subsection*{What is an observation of "no interaction"?}

@@

  A simple example will illustrate the problem: assume that we want to infer the probability of an interaction between two species, A and B. Now assume that in reality, interaction between A and B is completely impossible (i.e. the true $\lambda$= 0). Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal (very) little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1 (Fig.~\ref{upper_limits}). For 5 observations, this confidence limit will still extends to 0.5. Only with thirty observations will it shrink to 0.1. Thus, adding (many) more observations is certainly useful in controlling uncertainty due to stochasticity inherent in the process itself.

@@

@@

  % The bottom line is that separating different sources of uncertainty is difficult indeed. In the best of all possible worlds, we might use an experimental approach to estimate detection uncertainty by creating replicate cases where the interaction really occurs and then evaluating the fraction of cases where the interaction is detected. Yet, as anyone attempting these experiments will know, most interaction partners are notoriously unwilling to collaborate. Gallers refuse to lay eggs on their host plants in captivity (ref ref) and parasitoids decline to attack their hosts when experimentally introduced (Gariepy 2017; ref ref). If we introduce only one of the components (as in the cases where we expose a set of hosts to parasitism; ref ref; Gripenberg et al. xxx) then we are already confounding multiple levels of uncertainty since it is not certain whether the interaction will occur or whether we can detect it. To perform these experiments in a comprehensive and reliable manner, we will then need to replicate a large number of interactions in a comprehensive experiment across space. This type of “cafeteria experiments in space” is not only unfeasible, but also undermines our original objective: If the local occurrence of interactions is uninformative regarding the underlying probabilities of occurrence, then is not likely to be worthwhile collecting these local interaction matrices in the first place. <deep sigh and forget that section? >

  % As an alternative to abandoning empirical networks or continuing to ignore the uncertainty inherent in undetected observations, we propose that some insight regarding the detectability of interactions between species not found co-occurring may be gained from data on other species between which interactions are known to be feasible. If we use this information obtain the joint probability of detection and process (e.g. to glean information regarding at how many sites the species are found interacting across the entire dataset), and assuming that most of this pattern is due to variation in detection rate, then insights into the incidence of interactions between species may be gleaned from the accumulation rate of positive interactions at sites were interaction is possible (i.e. with at least one observation of a positive interaction) [this reasoning to be further formalised]

  % It is getting more and more common to represent interactions as probabilities in theoretical models of network structure. For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a gaussian probability function is used to represent the niche by~\citet{Williams2010}. \citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species. Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.,~\citealp{Rohr2016}). There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version~\citep{Poisot2016}. But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.

  To progressively dissect the different contributions to uncertainty, we will start by considering how we could naively quantify interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}. We consider that a pair of species have been observed $n$ times co-occurring at one location, and the number of times they have been observed interacting is $k = 0$. We now aim to evaluate the uncertainty of this interaction. The occurrence of an interaction is a Bernoulli trial. Consequently, the number of success $k$ over $n$ trials will follow a binomial distribution:

  \noindent The parameter $\lambda$, the probability of observing an interaction over an infinite time interval and area, is the quantity we want to estimate from empirical data. 
  The maximal likelihood estimate (MLE) of $\lambda$ is straightforward to find given $k$ and $n$:

  The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$). It is important to remember that this variance describes the variability of the number of success $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$.
  Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval} (for details, see [\citealp{}]). Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks. First, $\lambda$ is not a single point estimate but rather a random variable with a given uncertainty, the distribution of which is unknown. This means that even if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. What it implies is that no interaction is the most likely situation but there is nonetheless a significant chance that the two species \emph{could} interact. In contrast with the situation where $k>0$, when we are sure that an interaction is feasible, 
  % (in which case, the ratio $k/n$ is smaller than $n$ because of detection and process uncertainty),  % This parenthetical makes the sentence very long. Is it necessary?
  we are not sure that absence of interactions is caused by $L=0$. Second, and most importantly, the number of trials $n$ might be very low in many instances (and some pairs of species might not have been documented as co-occuring in even one case). Consequently, the uncertainty in the estimation of $\lambda$ might be considerable. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size. At a small sample size, the 95\% confidence interval spans all values of $\lambda$. To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting.
  % Is the Clopper-Pearson interval the one in Dom's code snippets? If so, this is Fig.~\ref{Salix_cdfs}

  The situation where $k = 0$ is also problematic because we have very little information with which to estimate $\lambda$, in particular when $n$ is also small. We therefore propose a Bayesian approach to solve this problem, building on two relevant features of such statistics: the posterior distribution of parameter estimates and usage of prior information. Before moving to this direction, we will first take time to better describe what is exactly meant by an interaction probability and appropriately define sources of uncertainty.

@@

      We here adopt a Bayesian approach to estimate the distribution of the parameter $\theta$, the maximum likelihood estimate of the interaction probability. According to Bayes principle, the posterior distribution of $\theta$ is:

@@

      \begin{figure}[ht]
        \label{Salix_pdfs}
        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-parasitoid networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting. Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution (N=0 observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times. The distribution narrows and approaches zero as the sample size increases. \textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-parasitoid component. This is likely because the prior distribution for the galler-parasitoid component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than the \emph{Salix}-galler component.}
        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
        \end{figure}

@@

          [Tomas adds: This is a bit of a stump]
          It is possible to estimate the probability of interaction between a pair of species if there is knowledge of their traits and some functions relating trait matching to interaction probability~\citep{Morales-Castilla2015}. There are several techniques available to perform this inference of interaction probability~\citep{} (REFS). Note that in this case the prior might not be beta distributed and numerical methods might be required to compute the posterior distribution.

@@

    The exercise exemplified above yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1 (recall Fig.~\ref{upper_limits}). Note the special case where there is no observation of the two species co-occurring and failing to interact, $n = 0$. In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should the co-occur; see above).

@@

    It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}. Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$; the remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one. It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics. Computation of these metrics involves non-linear functions and therefore, because of Jensen's inequality (which states that the average of non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty in $\lambda$s could bias both the mean and variance of a network metric. For instance, assume that among all pairs of species with few observed co-occurrence there are many pairs which truly interact.    If we begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution. While we can, as described above, calculate these network metrics using fixed estimates for $\lambda$ no analytical solution currently exists for uncertain $\lambda$. Instead we must rely on computer simulations. In the following section, we will provide an empirical example, based on the data set published by~\citet{Kopelke2017}. We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics. We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed fixed entities.

@@

      We use an extensively sampled \emph{Salix}-galler-parasitoid meta-network as a case study. This dataset consists of a single community type sampled across Europe, including willow (\emph{Salix}) species, willow-galling sawflies (Hymenoptera, Tenthredinidae, Nematinae, Euurina), and their natural enemies (hymenopteran parasitoids and coleopteran, lepidopteran, dipteran, and hymenopteran inquilines). The data was collected over 29 years (1982-2010) at 374 unique locations across Europe ranging from Sicily to the Arctic. Including repeated visits to a number of sites, the data set contains 641 site-visits, each of which can be considered as a network in its own right. Here we consider each network as an independent sample from which to build the meta-network. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes and 126 natural enemy nodes. Interactions were determined by dissecting and rearing gall inhabitants from 165,424 galls. The high spatiotemporal resolution of this network and the unusually high sampling effor implemented at the site level (641 site-visits, which can be considered as repeated samples of the network) makes this dataset particularly well suited for testing this method.

      Importantly, while large, this network will illustrate the very real constraints on the sampling of ecological networks. As a baseline pattern, we may compare the frequency of co-occurrence of taxa in the example data set to the pattern of Fig.~\citep{upper_limits}. In the example data, most (3986 out of 4992) pairs of species are never found co-occurring, and for species found co-occurring the number of co-occurrences was generally low (Fig.~\ref{histograms}A). Among the species which did sometimes interact when co-occurring, the incidence of interaction was actually low. Only 141 pairs of species were observed interacting: of these, 26 were observed interacting only once and 48.2\% were observed interacting five or fewer times (Fig.~\ref{histograms}B). Thus, even in the most extensive data set that we could think of, limited sampling is clearly a major source of uncertainty.

@@

      With species $i$ and $j$ co-occurring at all 374 sites and never being observed to interact, the maximum likelihood expectation for the probability of an interaction $ij$ is very close to 0 and the variance about this estimate is very narrow. In other words, we could establish with high certainty that the species will never interact. However, for most pairs of species $i$ and $j$, the species did not co-occur at so many sites and our posterior mean and variance retain some influence of the prior. Nevertheless, as the number of observed co-occurrence increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).

@@

      As well as obtaining posterior means and variances, it is possible to calculate a 95\% credible interval about the posterior mean. This is again straightforward to do in R (see the function ``credible interval" in \emph{Appendix S2}). Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrences without any observed interaction (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases. In no case, however, does the confidence interval include 0. Even for a pair of species which appeared together in all 374 sites but were never observed interacting, the confidence interval (0.001, 0.018) comes close to, but does not include zero (Table~\ref{interval_table}). In other words, even with a very large data set, we will have problems in establishing that a given species pair can never interact.

@@

      \begin{table}[h]
        \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Barbour2016,Barbour2016Dryad}. [Tomas notes that this is conceptually very similar to Fig.~\ref{Salix_pdfs}]}
        \label{interval_table}
        \begin{tabular}{l | c c | c c }
        \multirow{2}{*}{N} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-parasitoid}\\
         & Lower bound & Upper bound \\
        \hline
        0   & 0.152 & 0.931 & 0.008 & 0.364 \\
        1   & 0.110 & 0.843 & 0.007 & 0.337 \\
        2   & 0.087 & 0.760 & 0.006 & 0.313 \\
        5   & 0.053 & 0.573 & 0.005 & 0.258 \\
        10  & 0.033 & 0.400 & 0.004 & 0.200 \\
        15  & 0.023 & 0.306 & 0.003 & 0.163 \\
        20  & 0.018 & 0.247 & 0.003 & 0.137 \\
        25  & 0.015 & 0.208 & 0.002 & 0.119 \\
        50  & 0.008 & 0.115 & 0.001 & 0.071 \\
        100 & 0.004 & 0.061 & 0.001 & 0.039 \\
        150 & 0.003 & 0.041 & \textless0.001 & 0.027 \\
        200 & 0.002 & 0.031 & \textless0.001 & 0.021 \\
        \hline
        374 & 0.001 & 0.017 & \textless0.001 & 0.011 \\
        \hline
        \end{tabular}
        \end{table}

@@

\section*{Conclusions/recommendations}
